% !TeX spellcheck = en_US
%%% The main file. It contains definitions of basic parameters and includes all other parts.

%% Settings for single-side (simplex) printing
% Margins: left 40mm, right 25mm, top and bottom 25mm
% (but beware, LaTeX adds 1in implicitly)
%\documentclass[12pt,a4paper]{report}
%\setlength\textwidth{145mm}
%\setlength\textheight{247mm}
%\setlength\oddsidemargin{15mm}
%\setlength\evensidemargin{15mm}
%\setlength\topmargin{0mm}
%\setlength\headsep{0mm}
%\setlength\headheight{0mm}
% \openright makes the following text appear on a right-hand page
%\let\openright=\clearpage

% set fonts
%\renewcommand{\ttdefault}{Lucida Sans Typewriter}

%% Settings for two-sided (duplex) printing
 \documentclass[12pt,a4paper,twoside,openright]{report}
 \setlength\textwidth{145mm}
 \setlength\textheight{247mm}
 \setlength\oddsidemargin{14.2mm}
 \setlength\evensidemargin{0mm}
 \setlength\topmargin{0mm}
 \setlength\headsep{0mm}
 \setlength\headheight{0mm}
 \let\openright=\cleardoublepage

%% Generate PDF/A-2u
\usepackage[a-2u]{pdfx}

%% Character encoding: usually latin2, cp1250 or utf8:
\usepackage[utf8]{inputenc}

%% Prefer Latin Modern fonts
\usepackage{lmodern}

%% Further useful packages (included in most LaTeX distributions)
\usepackage{amsmath}        % extensions for typesetting of math
\usepackage{mathtools}
\usepackage{amsfonts}       % math fonts
\usepackage{amsthm}         % theorems, definitions, etc.
\usepackage{bbding}         % various symbols (squares, asterisks, scissors, ...)
\usepackage{bm}             % boldface symbols (\bm)
\usepackage{graphicx}       % embedding of pictures
\usepackage{fancyvrb}       % improved verbatim environment
\usepackage{natbib}         % citation style AUTHOR (YEAR), or AUTHOR [NUMBER]
\usepackage[nottoc]{tocbibind} % makes sure that bibliography and the lists
			    % of figures/tables are included in the table
			    % of contents
\usepackage{dcolumn}        % improved alignment of table columns
\usepackage{booktabs}       % improved horizontal lines in tables
\usepackage{paralist}       % improved enumerate and itemize
\usepackage[usenames]{xcolor}  % typesetting in color

\usepackage{algpseudocode}  % for typeseting algorithms
\usepackage{algorithm}	 	% for typeseting algorithms
\usepackage{physics}        % derivatives

\usepackage{minted}		% syntax highlight
%\usepackage{tcolorbox}	% tools for modifying minted environment
%\usepackage{etoolbox}
%\BeforeBeginEnvironment{minted}{\begin{tcolorbox}}%
%\AfterEndEnvironment{minted}{\end{tcolorbox}}%

\usepackage[american,siunitx]{circuitikz}		% circuit diagrams, use 'american' for US symbols
\usepackage{subcaption}
\usepackage{makecell}	    % line breaks inside table cell
\usepackage{tabu}
\usepackage{longtable}

% libraries for TikZ
\usetikzlibrary{arrows,decorations.markings}
%%% Basic information on the thesis

% Thesis title in English (exactly as in the formal assignment)
\def\ThesisTitle{NextGen SPICE – Electrical Circuit Simulation Library for .NET}
\def\ThesisTitleCz{NextGen SPICE – knihovna pro simulaci elektrických obvodů pro .NET}

% Author of the thesis
\def\ThesisAuthor{Radek Zikmund}

% Year when the thesis is submitted
\def\YearSubmitted{2018}

% Name of the department or institute, where the work was officially assigned
% (according to the Organizational Structure of MFF UK in English,
% or a full name of a department outside MFF)
\def\Department{Department of Distributed and Dependable Systems}

% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Department}

\def\DeptTypeCz{Katedra}


% Thesis supervisor: name, surname and titles
\def\Supervisor{Mgr. Pavel Ježek, Ph.D.}

% Supervisor's department (again according to Organizational structure of MFF)
\def\SupervisorsDepartment{Department of Distributed and Dependable Systems}
\def\SupervisorsDepartmentCz{Katedra distribuovaných a spolehlivých	systémů}

% Study programme and specialization
\def\StudyProgramme{Computer Science}
\def\StudyBranch{Programming and Software Systems}

% An optional dedication: you can thank whomever you wish (your supervisor,
% consultant, a person who lent the software, etc.)
\def\Dedication{%
	I would like to thank my supervisor \Supervisor{} for his time, patience and the advice he gave me during our consultations. Also, special thanks go to my family, friends and everybody who supported me and helped me during my studies.
}

% Abstract (recommended length around 80-200 words; this is not a copy of your thesis assignment!)
\def\Abstract{%	
	The goal of this thesis was to create an extensible library for simulating electrical circuits for the .NET platform, which could be used in broad contexts like development of educational programs or applications that use evolutionary algorithms to evolve electrical circuits. Our library is inspired by the family of SPICE programs developed at University of California, Berkeley.
	
	The initial version of our library implements transient analysis of electrical circuits and supports basic devices like voltage and current sources, resistors, capacitors, inductors, but also semiconductor diode and BJT transistor devices. Our library is designed in such a way that both new circuit devices and circuit analyses can be added in future versions.
	
	Other features of our library include importing circuits or their parts from industry standard SPICE netlists and the ability to modify circuit parameters during the simulation. In this thesis, we also investigate using the double-double precision type to improve convergence during the simulation.
		
	We also implement a simple SPICE-like console application to allow our simulation library to be used from the command line.
}

% 3 to 5 keywords (recommended), each enclosed in curly braces
\def\Keywords{%
	{Electrical circuit simulation} {SPICE} {.NET} {Library}
}

% Abstract (recommended length around 80-200 words; this is not a copy of your thesis assignment!)
\def\AbstractCz{%
	Cílem této práce bylo vytvořit rozšiřitelnou knihovnu pro simulaci elektrických obvodů pro platformu .NET, která by byla uplatnitelná v širokém kontextu, jako je vývoj výukových programů nebo aplikací využívajících evolučních algoritmů pro evoluci elektrických obvodů. Naše knihovna je inspirována rodinou SPICE programů vyvíjených na Kalifornské univerzitě v Berkeley.
	
	Počáteční verze naší knihovny implementuje transientní analýzu elektrických obvodů a podporuje základní součástky jako zdroje napětí a proudu, rezistory, kondenzátory a cívky, ale také polovodičové diody a BJT transistory. Naše knihovna je navržena takovým způsobem, že je možné v budoucích verzích knihovny přidat jak nové součástky, tak nové typy analýz.
	
	Další vlastnosti naší knihovny zahrnují importování obvodů nebo jejich částí v průmyslově standardním SPICE netlist formátu a možnost upravovat parametry součástek během simulace. V této práci také prověřujeme použití typů s přesností double-double pro zlepšení konvergence během simulace.
	
	Také jsme implementovali jednoduchou SPICE-like konzolovou aplikaci abychom umožnili používání naší simulační knihovny z příkazové řádky.
}

% 3 to 5 keywords (recommended), each enclosed in curly braces
\def\KeywordsCz{%
	{Simulace elektrických obvodů} {SPICE} {.NET} {Knihovna}
}

%% The hyperref package for clickable links in PDF and also for storing
%% metadata to PDF (including the table of contents).
%% Most settings are pre-set by the pdfx package.
\hypersetup{unicode}
\hypersetup{breaklinks=true}

% Definitions of macros (see description inside)
\include{macros}

% Title page and various mandatory informational pages
\begin{document}
\include{title}

%%% A page with automatically generated table of contents of the bachelor thesis

\tableofcontents

%% Set path for pictures
\graphicspath{ {../img/} }
\usemintedstyle{colorful}

%%% Each chapter is kept in a separate file
%\include{preface}
\include{chap-introduction}
\include{chap-spicecode}
\include{chap-analysis}
\include{chap-devdocs}
\include{chap-userdocs}
\include{chap-results}

%%%%%%%%

%%%%%%%%

\include{epilog}

%%% Bibliography
\include{bibliography}

%%% Figures used in the thesis (consider if this is needed)
%\listoffigures

%%% Tables used in the thesis (consider if this is needed)
%%% In mathematical theses, it could be better to move the list of tables to the beginning of the thesis.
%\listoftables

%%% Abbreviations used in the thesis, if any, including their explanation
%%% In mathematical theses, it could be better to move the list of abbreviations to the beginning of the thesis.
%\chapwithtoc{List of Abbreviations}

%%% Attachments to the bachelor thesis, if any. Each attachment must be
%%% referred to at least once from the text of the thesis. Attachments
%%% are numbered.
%%%
%%% The printed version should preferably contain attachments, which can be
%%% read (additional tables and charts, supplementary text, examples of
%%% program output, etc.). The electronic version is more suited for attachments
%%% which will likely be used in an electronic form rather than read (program
%%% source code, data files, interactive charts, etc.). Electronic attachments
%%% should be uploaded to SIS and optionally also included in the thesis on a~CD/DVD.
%%% Allowed file formats are specified in provision of the rector no. 23/2016.
\include{attachments}

\openright
\end{document}
